Approximation as Differentiation notes

### 2025-02-09 notes.tex
Remove ACM ref, build twice to remove temp page.
Start on category of families.

@@

>>>>

\input{macros}

\settopmatter{printacmref=false}

@@

\section{Overview}

Some notes on the key constructions:
\begin{itemize}
\item Categories of families, special case of Grothendieck construction
\end{itemize}

\section{Definitions}

\subsection{Category of families}

Special case of Grothendieck construction for a functor $F: C \to \Cat$, where we consider the special case
where $F: C \to \Set$. (This is a ``special case'' inasmuch as there is an embedding from $\Set$ to $\Cat$
sending each set to the corresponding discrete category.)
